Centrality and Activity for Envolving Networks

### 2013-06-20 network-science/paper.tex
5

\begin{document}
\maketitle
\newpage
\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered to be vertex while friendship is considered to be edge. We
suppose the evolution of a social network overtime only includes bidirectional
new connections between exsisting or newly created nodes, and we assume the
graph will evolve as a typical social network. We study the centrality and
activity metrics for nodes in such graphs by regulate a series of reasonable
properties the metrics should satisfy. We then formally define our metrics and
give their mathematical analysis. We have developped a practical based
framework to maintain the evolving network and the algorithm to compute our
metrics with preferable time and space consumption, including historical
queries. Finally, we put the result of experiment with a couple of authentic
data.

\textbf{Keywords.} social network, dynamic graph, centrality, activity, algorithm. 
\end{abstract}

>>>>

\begin{document}
\maketitle
\newpage
\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered as vertex while friendship is considered as edge. We suppose the
evolution of a social network overtime only includes bidirectional new
connections between existing or newly created nodes, and we assume the graph
will evolve as a typical social network. We study the centrality and activity
metrics for nodes in such graphs by regulate a series of reasonable properties
the metrics should satisfy. We then formally define our metrics and give their
mathematical analysis. We have developed a practical based framework to
maintain the evolving network and the algorithm to compute our metrics with
preferable time and space consumption, including historical queries. Finally,
we put the result of experiment with a couple of authentic data.

\smallskip
\noindent \textbf{Keywords.} social network, dynamic graph, centrality,
activity, algorithm.
\end{abstract}
